\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2012-11-15 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
adds the description of NGNOD in the user manuel; updates Makefile.in

>>>>

\item [{\texttt{NGNOD}}] The number of nodes for 2D and 3D shape functions for hexahedra. We use either 
8-node mesh elements (bricks) or 27-node elements. If you use the internal mesher, the only option is 8-node bricks 
(27-node elements are not supported). \texttt{CUBIT} does not support HEX27 elements either (it can generate them, 
but they are flat, i.e. identical to HEX8). To generate HEX27 elements with curvature properly taken into account, 
you can use \texttt{Gmsh} \url{http://geuz.org/gmsh/}
